---
title: "Kuala Lumpur Composite Index Futures (FKLI)"
author: "HweeSee Teh"
date: "April 27, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The Source of the Data

- The dataset used is a live data that refreshed daily which consists of market history for Kuala Lumpur Composite Index Futures (FKLI) in year 2017. - The data is provided by an exchange holding company in Malaysia, BURSA Malaysia. 
- The data retrieval API was privided by Quandl API.  
- The data can be validated against [Historical Data in BURSA Market Statistics](http://www.bursamalaysia.com/market/derivatives/market-statistics/historical-data/).  

## The Dataset  
```{r installprerequisite, echo=FALSE, include=FALSE}
#install.packages("plotly")
library(plotly)
#install.packages("Quandl")
library(Quandl)
library(dplyr)
```  
  
```{r gettingdate, echo=FALSE}
stockdata <- Quandl("MYX/FKLIU2017", api_key="cwsM4nx544ZcQkhDngzn")
str(stockdata)
```  

## The plot  
The plot is creatred using plotly.  
```{r stockplot}
myplot <- plot_ly(stockdata) %>%
  add_trace(x = ~Date, y = ~Volume, type = 'bar', name = 'Volume', 
            marker = list(color = '#C9EFF9'),
            hoverinfo = "text",
            text = ~Volume) %>%
  add_trace(x = ~Date, y = ~High, name = 'High', type = 'scatter', mode = 'lines+markers', yaxis = 'y2') %>%
  add_trace(x = ~Date, y = ~Low, name = 'Low', type = 'scatter', mode = 'lines+markers', yaxis = 'y2') %>%
  add_trace(x = ~Date, y = ~Settle, name = 'Settle', type = 'scatter', mode = 'lines+markers', yaxis = 'y2') %>%
  layout(title = 'Kuala Lumpur Composite Index Futures (FKLI) 2017',
         xaxis = list(title = "Date"),
         yaxis = list(side = 'left', title = 'Volume', showgrid = FALSE, zeroline = FALSE),
         yaxis2 = list(side = 'right', title = 'Market Price', overlaying = "y", 
         showgrid = FALSE, zeroline = FALSE)
         ) %>%
  layout(legend = list(x = 1.1, y = 0.9))
myplot
```  

## The End  
Thanks you!
